Location and Scale-Invariant Power Transformations for Transforming Data to

### 2025-10-25 manuscript_rmarkdown/manuscript.Rmd
Make definition of central normal distribution clearer.

\begin{definition}[Centrally normal distribution]

A centrally normal distribution is any distribution whose quantile function is 
defined by $F^{-1}_{\mathcal{N}}$ for $\frac{1-\kappa}{2} \leq  p \leq \frac{1 + \kappa}{2}$,
with $\mathcal{N}$ any normal distribution.

@@

If the sum of residual errors of the central portion of a sequence is 0, i.e.,
$\sum_{r_j \in \mathbf{R}_{\text{c}}} r_j = 0$, 
the values of the elements in the central portion of that sequence follow a 
centrally normal distribution.

@@

By the Glivenko-Cantelli theorem, if sequence $\mathbf{X}$ was sampled from a
normal distribution $\mathcal{N}(\mu, \sigma)$,
$\lim_{n \rightarrow \infty} \sum_{r_j \in \mathbf{R}_{\text{c}}} r_j = 0$,
i.e. an infinite sequence sampled from a normal distribution has a central portion
with values sampled from a centrally normal distribution.

\begin{definition}[Central normality test]
The null-hypothesis $\mathcal{H}_0$ is that the sequence $\mathbf{X}$ was sampled
from a population that has a centrally normal distribution.

The alternative hypothesis is that the sequence $\mathbf{X}$ was sampled from a
population that lacks a centrally normal distribution.
\end{definition}

@@

The null-hypothesis should be rejected at significance level $\alpha$ if 
$\tau_{n, \kappa} \geq \tau_{\alpha, n, \kappa, \zeta, \text{critical}}$,
with $\zeta$ the population estimate of the rate of outliers. Critical test
values are determined in the [Simulation](#simulation) section.

>>>>

\begin{definition}[Central normal distribution]

A central normal distribution is any distribution whose quantile function is 
defined by $F^{-1}_{\mathcal{N}}$ for $\frac{1-\kappa}{2} \leq  p \leq \frac{1 + \kappa}{2}$,
with $\mathcal{N}$ any normal distribution.

@@

For $\kappa = 1.0$, the central normal distribution is a normal distribution.

@@

By the Glivenko-Cantelli theorem, if a sequence $\mathbf{X}$ was sampled from a
central normal distribution, then almost surely
$\lim_{n \rightarrow \infty} \sum_{r_j \in \mathbf{R}_{\text{c}}} r_j = 0$,

\begin{definition}[Central normality test]
The null-hypothesis $\mathcal{H}_0$ is that the sequence $\mathbf{X}$ was sampled
from a population that is distributed according to a central normal distribution.

The alternative hypothesis is that the sequence $\mathbf{X}$ was sampled from a
population that is not distributed according to a central normal distribution.
\end{definition}

@@

The null-hypothesis should be rejected at significance level $\alpha$ if 
$\tau_{n, \kappa} \geq \tau_{\alpha, n, \kappa, \zeta, \text{critical}}$,
with $\zeta$ the population estimate of the rate of outliers from a normal
distribution, to be defined in the [Simulation](#simulation) section.
